Speed and strength of an epidemic intervention

### 2020-06-20 doc/speedstrength.tex
Edit significance

\documentclass[12pt]{article}
\usepackage[]{graphicx}
\usepackage[]{color}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

@@

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage[]{color}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

@@

\section*{Significance statement}

Researchers studying infectious-disease outbreaks often focus primarily on the reproductive number, which measures the “strength” of transmission – the number of new infections caused by an infectious individual.
Much less theoretical and modeling attention is paid to the exponential growth rate, which measures epidemic “speed”. 
We argue that this difference in emphasis is largely artificial: both strength and speed have thresholds for spread, and both provide frameworks to compare potential for spread to effectiveness of intervention.
We generalize the classic strength-based paradigm and show that there is a corresponding speed-based paradigm which can provide complementary insights.
We provide specific examples from important diseases, including rabies and HIV, to demonstrate the value of both perspectives.
